Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-05-28 paper.tex
abstract improved
abstract
need to do a final touch once we have all the models in

%In recent years, similar features between small systems like proton-proton (pp) collisions and large systems like lead-lead collisions have been observed via long-range correlations in pseudorapidity (so-called the ridge) for pairs of charged hadrons. Many theoretical approaches have been applied to interpret the similarity. However, it is still controversial whether the ridge in small systems is originated from initial or final-state effects of the collision.

To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV with ALICE. The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016. Jet events are selected by two methods. The first one is done by seeing the transverse momentum of  leading particle in the pseudorapidity range $|\eta|<0.9$. The second method is done by reconstruction of charged jets using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. The measured ridge yield is consistent with the previous results from other LHC experiments. Furthermore, the ridge yield is found to be independent of the energy scale of the hard scattering process. This observation can help identify the origins of the ridge in small systems.

>>>>

Long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by the ALICE experiment at the Large Hadron Collider. 
These results are obtained in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class.
In addition to the conventional long-range correlation studies, the results are further investigated in events, where jets with harder fragmentations is to be present.
The jets are reconstructed by using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. 
The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events. 
These correlations also persists in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $p_{\mathrm T, jet} > 10$~GeV/$c$.
The results are compared to PYTHIA8 string shoving, EPOS and A Multi-Phase Transport ({AMPT}) model calculations.  
PYTHIA8 string shoving model can describe low $p_{\mathrm T}$  ridge yields but can't give good description of  $p_{\mathrm T}$ dependence both for the unbiased and jet events.
The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.
